\cvsection{Experience}
\begin{cventries}
\cventry{
	    CIB Macro Electoronic Trading Technology
    }
    {Sr Lead Software Engineer | Macro eTrading Commodities Derivatives | Vice President }
    {JP Morgan|Singapore}
    {Jan. 2022 - Current}
    {
      \begin{cvitems}
        \item {Built PnL circuit breakers that controls pricing for electronic market making (EMM) commodities strats}
        \item {Built Realtime PnL calculation engine from market price, client and hedge trades }
        \item {Built airbags that controls the bid and ask spread from desk. Airbag triggers during high volatility in market price }
        \item {Various small enhancements that supports commodities EMM on Order Management and Price Delivery}
      \end{cvitems}
    }
\cventry{
	    CIB Post Trade Technology
    }
    {Software Engineer |  Asset Movement Engine | Vice President }
    {JP Morgan|Singapore}
    {Jun. 2013 - Dec. 2021}
    {
      \begin{cvitems}
        \item {Lead developer for cleared derivatives settlement processing in Asset Movement Engine.}
        \item {Built and on-boarded cleared derivatives margin and brokerage settlements}
        \item {Uplift of legacy payment system that moved few billion USD every day to strategic Asset Movement Engine.}
        \item {Built and managed 100s of automated regression end to end tests to ensure no change breaks production. }
        \item {Developed time sensitive eod of day liquidity report for FED that is backed by millions of equity trades }
      \end{cvitems}
    }
\cventry{
	    Markets Technology
    }
    {Java Developer | InMemory Data Grid}
    {ANZ|Singapore}
    {Sep. 2011 - Jun. 2013}
    {
      \begin{cvitems}
        \item {Built TradeRepository for OTC trades  supports Rates, FX, and Commodities using Gemfire NoSQL InMemory Data Grid.}
        \item {Monte-Carlo simulation engine accesses data using 1000 core HPC grid.}
        \item {Developed an automated testing framework to replay 1000s of combinations of OTC Trade lifecycle.}
        \item {Developed C# based Excel Plugin to make comprehensive query on data grid using Excel-DNA}
      \end{cvitems}
    }
\cventry{
	    Investment Banking - Equities Trading Technology
    }
    {Java Developer | Realtime Front office position service}
    {Credit Suisse |Singapore}
    {Jun. 2010 - Jun. 2013}
    {
      \begin{cvitems}
        \item {Built position management system used by traders and algo trade engines for net position, realized and unrealized PnL, and equity risk calculations}
        \item {Developed trade sources that ingress 4k trades per second from order management systems (OMS) that originated from Exchange connectivity}
        \item {Designed and developed in-memory position and PnL calculation using Oracle Coherence Data Grid }
        \item {JVM profiling and Garbage Collection tuning with visualVM.}
      \end{cvitems}
    }
\cventry{
	    Private Banking Technology
    }
    {Java Developer | Enterprise Architect Associate }
    {Credit Suisse |Singapore}
    {Jun. 2007 - May. 2010}
    {
      \begin{cvitems}
        \item {Built client relationship manager portal for APAC franchaise }
        \item {Built Post Execution Pre Settlement matching engine using Omgeo API interfacing with external brokers }
        \item {SOAP based Java services for Temeonos Core banking platform }
       \end{cvitems}
    }

\end{cventries}
